Forecasting League of Legends Player Performance through In-Game Metrics and Key Statistics

### 2024-11-27 paper/paper.qmd
add datasheet and appendix

This paper developing a hybrid model that leverages both traditional in-game metrics and advanced variables, such as total creep score (CS), to forecast player performance for BLG in the 2024 season. The model specifically focuses on predicting the Kill-Death-Assist ratio (KDA), a widely accepted indicator of individual performance, across various matches. Finally offers actionable insights into player roles and impacts, highlighting those who can consistently carry games and identifying players whose performance may not justify their perceived value.

The remainder of this paper is structured as follows: @sec-data provides an overview of the data. @sec-model provides the modeling approach, including simple and multiple linear regression models and a Bayesian hierarchical model. We then present our results in @sec-result and discuss the implications, limitations, then we predict the election in @sec-prediction, and future research directions in @sec-discussion.

@@

the data gathering and analysis is done in R [@citeR] with the following packages: knitr [@knitr], tidyverse [@tidyverse], ggplot2 [@ggplot2], dplyr [@dplyr], arrow [@arrow], here [@here], and Rstan [@Rstan]

@@

# Display in multiple columns with kable
kable(column_df, format = "latex", booktabs = TRUE, col.names = NULL)
```

@@

```{r}
#| echo: false
#| warning: false

# # Add predictions to the data
# cleaned_lol_data$predicted_KDA <- apply(bayesian_model_predictions, 2, mean) # Take the mean of posterior predictions

# # Create a visualization with actual vs. predicted values
# ggplot(cleaned_lol_data, aes(x = damagetochampions)) +
#   geom_line(aes(y = KDA, color = "Actual"), size = 1) + # Line for actual values
#   geom_line(aes(y = predicted_KDA, color = "Predicted"), size = 1, linetype = "dashed") + # Line for predicted values
#   labs(
#     title = "Actual vs Predicted KDA",
#     x = "Game Index",
#     y = "KDA",
#     color = "Legend"
#   ) +
#   theme_minimal() +
#   theme(
#     legend.position = "bottom"
#   )

@@

```{r}
print(r_squared)
```

@@

@@

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

>>>>

This paper developing a hybrid model that leverages both traditional in-game metrics and advanced variables, such as total creep score (CS, you kill the minion in the game, higher cs means earned more gold from killing minions), to forecast player performance for BLG in the 2024 season. The model specifically focuses on predicting the Kill-Death-Assist ratio (KDA), a widely accepted indicator of individual performance, across various matches. Finally offers actionable insights into player roles and impacts, highlighting those who can consistently carry games and identifying players whose performance may not justify their perceived value.

The remainder of this paper is structured as follows: @sec-data provides an overview of the data. @sec-model provides the modeling approach, including simple and multiple linear regression models and a Bayesian hierarchical model. We then present our results in @sec-result and discuss the implications and limitation, future research directions in @sec-discussion.

@@

the data gathering and analysis is done in R [@citeR] with the following packages: knitr [@knitr], tidyverse [@tidyverse], ggplot2 [@ggplot2], dplyr [@dplyr], arrow [@arrow], here [@here], kableExtra[@citekableextra], and Rstan [@Rstan]

@@

# Display in multiple columns with kable
# Generate the table and allow it to span multiple pages
kable(column_df, format = "latex", booktabs = TRUE, longtable = TRUE) %>%
  kable_styling(latex_options = c("repeat_header")) # Adds headers to each new page

@@

@@

```{r}
#| echo: false
#| warning: false
print(r_squared)
```

@@

\appendix

@@

# Model Detail

## Trace Plot

```{r}
#| label: fig-bayesian-model-trace-plot
#| fig-cap: "The figure capture the trend of actual player KDA performance"
#| echo: false
#| warning: false

# Add predictions to the data
bayesian_model_predictions_geoline = posterior_predict(bayesian_model_1, newdata = cleaned_lol_data)
geo_line_visualization_dataset = cleaned_lol_data
geo_line_visualization_dataset$predicted_KDA <- apply(bayesian_model_predictions_geoline, 2, mean) # Take the mean of posterior predictions

# Create a visualization with actual vs. predicted values
ggplot(geo_line_visualization_dataset, aes(x = damagetochampions)) +
  geom_line(aes(y = KDA, color = "Actual"), size = 1) + # Line for actual values
  geom_line(aes(y = predicted_KDA, color = "Predicted"), size = 1, linetype = "dashed") + # Line for predicted values
  labs(
    title = "Actual vs Predicted KDA",
    x = "damagetochampions",
    y = "KDA",
    color = "Legend"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom"
  )

# Ideal Survey

An ideal survey for studying esports performance and its impact on players, teams, and audiences would involve a structured and systematic approach. The goal is to collect comprehensive, representative, and high-quality data to inform further research and practical decision-making. Below is a detailed breakdown of the components of this survey:

## Sampling Frame

The sampling frame would include key stakeholders in the esports ecosystem, such as professional players, coaches, team managers, analysts, and dedicated fans. The survey would target participants across different regions, leagues (e.g., LPL, LCK, LEC, and LCS), and tiers of competitive play to ensure diversity and inclusivity. By including individuals with varied roles and perspectives, the survey would capture the multifaceted nature of esports performance and its broader implications.

## Survey Sending Process

The survey would be disseminated via multiple channels to maximize reach and response rates. Online platforms such as email, social media, and messaging apps like Discord and WhatsApp would be primary distribution methods for participants already active in esports communities. Partnerships with esports organizations, event organizers, and content creators would help promote the survey to a broader audience. Reminders would be sent periodically to encourage participation while ensuring ethical practices, such as respecting participants' privacy and obtaining informed consent.

## Sampling Methodology

The survey would adopt a stratified random sampling methodology to ensure representation across different stakeholder groups and regions. For example, participants would be grouped by roles (players, coaches, fans) and leagues, and then randomly selected from each group. This approach would mitigate biases and provide a balanced dataset that reflects the diversity of the esports ecosystem. Additionally, oversampling underrepresented groups, such as amateur players or smaller regional leagues, would ensure their voices are adequately captured.

## Survey Implementation & Question Creation

The survey would be implemented using a user-friendly online platform to ensure accessibility. Questions would be designed to address both qualitative and quantitative aspects of esports performance. For instance:
- **Quantitative Questions**: Metrics-based questions, such as training hours, in-game performance statistics, and viewership demographics.
- **Qualitative Questions**: Open-ended questions on the challenges faced by players, the impact of game patches, or perceptions of team dynamics and fan engagement.

Pilot testing would be conducted to refine the survey, ensuring questions are clear, unbiased, and aligned with the research objectives. Additionally, anonymity and confidentiality would be emphasized to encourage honest and accurate responses.

This structured approach to survey design and implementation would enable the collection of comprehensive and reliable data, supporting future research and actionable insights in the esports industry.

## Survey Questions

List of all of the questions:

1. Select your most play position in League of Legend
   - Top
   - Jungle 
   - Mid 
   - Bot 
   - Support

2. Please select your highest rank level
    - Unranked  
    - Iron  
    - Bronze  
    - Silver  
    - Gold  
    - Platinum  
    - Diamond  
    - Master  
    - Grandmaster  
    - Challenger

3. Please select the highest degree of education you have obtained
    - Summoner’s Rift (Ranked/Normal)  
    - ARAM (All Random All Mid)  
    - Teamfight Tactics (TFT)  
    - Ultimate Spellbook  
    - Nexus Blitz  
    - Custom Games  
    - Other (Please specify): __________

4. Which League of Legends esports league do you primarily watch, subscribe to, or focus on?

    - League of Legends Pro League (LPL)  
    - League of Legends Champions Korea (LCK)  
    - League of Legends European Championship (LEC)  
    - League Championship Series (LCS)  
    - Pacific Championship Series (PCS)  
    - Vietnam Championship Series (VCS)  
    - League of Legends Continental League (LCL)  
    - CBLOL (Brazilian League of Legends Championship)  
    - LJL (League of Legends Japan League)  
    - Other (Please specify): __________

5. Which is your favorite League of Legends (LoL) esports team?
    - T1  
    - JD Gaming (JDG)  
    - Bilibili Gaming (BLG)  
    - Gen.G  
    - G2 Esports  
    - Fnatic (FNC)  
    - Cloud9 (C9)  
    - Royal Never Give Up (RNG)  
    - DAMWON Gaming (DWG KIA)  
    - Team Liquid (TL)  
    - Other (Please specify): __________

6. Who do you consider to be the GOAT (Greatest of All Time) of League of Legends?
    - Faker (T1)  
    - Uzi (RNG)  
    - Bin (BLG)
    - Caps (G2 Esports)  
    - Other (Please specify): __________  
    - I’m not sure / I don’t have an opinion.

7. Who do you consider to be the best Top Laner of all time in League of Legends?
    - TheShy (Weibo Gaming)  
    - Zeus (T1) 
    - Marin (Retired)  
    - Nuguri (Retired)  
    - Smeb (Retired)  
    - Bin (Bilibili Gaming)  
    - 369 (JD Gaming)  
    - Impact (Evil Geniuses)  
    - Other (Please specify): __________  
    - I’m not sure / I don’t have an opinion.

8. How long have you been playing League of Legends?
    - Less than 6 months  
    - 6 months to 1 year  
    - 1–3 years  
    - 3–5 years  
    - 5–10 years  
    - Over 10 years

9. How often do you watch professional League of Legends games?
    - Rarely or never
    - A few matches per season
    - Regularly during major tournaments (e.g., Worlds, MSI)
    - Frequently during regional leagues (e.g., LPL, LCK)
    - I watch almost all professional games

10. Do you feel League of Legends has positively impacted your personal skills or habits?
    - Yes, it has improved my teamwork and communication skills
    - Yes, it has enhanced my problem-solving and decision-making abilities
    - Yes, it has boosted my resilience and mental toughness
    - No, I don’t feel it has impacted me personally
    - Other (Please specify): __________
